---
title: "r4ds_communicate_exercises_27"
output: html_document
---

# 27.2.1

1.  I did it
2.  I did it
3.  R notebook show output inside of editor. R markdown shows output in the console.
4.  The output and intermediate files are different. The input difference is the output in the YAML header `word_document`, `pdf_document` and `html_document`

# 27.3.1

## Jared Stier

----

### Education
*  __2015__  NCSU, B.S. in Mechanical Engineering

--------

### Employment
* __2015 - Current__ Red Ventures, Paid Media Associate

2.  Using the R Markdown quick reference, figure out how to
  * Go see my footnote at the bottom^[Here's my footnote]  
  * This is a horizontal rule below
  
  ------
  
  * >This is a block quote
  
3.  

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

Looks like a lot of values are rounded to the tenth's place
  
# 27.4.7
1.  

```{r, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```


```{r}

ggplot(diamonds) + 
  geom_bar(mapping = aes(x = cut))

```


```{r}
ggplot(diamonds) + 
  geom_bar(mapping = aes(x = color))

```

```{r}
ggplot(diamonds) + 
  geom_bar(mapping = aes(x = clarity))

```

2.  

```{r}
knitr::kable(
  arrange(diamonds, desc(carat))[1:20,1:4],
  caption = '20 Largest Diamonds'
)


```

3. 

```{r, warning=FALSE, message=FALSE}
library(scales)
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01) +
  scale_y_continuous(label = comma)

print(paste(comma(nrow(filter(diamonds, carat > 2.5))/nrow(diamonds),digits=2), '% of diamonds are larger than 2.5 carats',sep=''))


```

4.

```{r a, cache=TRUE}
thedate <- lubridate::now()
print(thedate)

```

```{r b, cache=TRUE}
thedate2 <- thedate
print(thedate2)

```

```{r c, cache=TRUE}
thedate3 <- thedate2
print(thedate3)

```

```{r d, cache=TRUE}
thedate4 <- thedate3
print(thedate4)

```



