---
title: "r4ds_communicate_exercises_28"
author: "Jared Stier"
date: "November 12, 2017"
output: html_document
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
```

# 28.2.1

## 1. 
```{r}
ggplot(mpg, aes(x = year, y = hwy, color = class)) + 
  geom_point() + 
  labs(
    x = 'Model Year',
    y = 'Highway MPG',
    title = 'MPGs Through the Years',
    subtitle = 'Well, I thought this would be interesting. Whoops',
    color = 'Car Class'
  )

```

## 2.
```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = class)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Fuel efficiency decreases with engine size",
    subtitle = "Subcompact cars are the most sensitive to engine size"
  )

```

## 3.
I haven't made any exploratory graphics in the past month. Sorry

# 28.3.1

## 1. 
```{r}
label <- tribble(
  ~displ, ~hwy, ~label, ~vjust, ~hjust,
     Inf,  Inf,    "Top right", "top", "right",
     Inf, -Inf,    "Bottom right", "bottom", "right",
    -Inf,  Inf,    "Top left", "top", "left",
    -Inf, -Inf,    "Bottom left", "bottom", "left"
)

ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_text(aes(label = label, vjust = vjust, hjust = hjust), data = label)

```

## 2.
`Annotate()` has arguments like aesthetic mappings that can be used to place your text

## 3.
If you add a label, it gets applied to all facets by default. 
To add the label to just one facet, include it as part of your label tibble. Ex:
```
label <- tibble(
  displ = Inf,
  hwy = Inf,
  class = "2seater",
  label = "Something about 2 seaters"
)
```
## 4.
* `label.padding ` adds padding
* `label.r` rounds the corners
* `label.size` changes the size of the label border

## 5.
Four arguments to arrow are:

* `angle`: angle of arrow head
* `length`: length of arrow head
* `ends`: ends of the line to draw arrow head
* `type`: open or close, whether the arrow head is open or closed.

# 28.4.4

## 1. 
You gotta use the fill aesthetic, not color. 

## 2.
First argument to every scale is the label. It's just like `labs()`

## 3.
```{r}
years <- lubridate::make_date(seq(year(min(presidential$start)),
             year(max(presidential$end)),
             by = 4), 1, 1)

presidential %>%
  mutate(id = 33 + row_number(),
         name_id = stringr::str_c(name, ' (', id, ')'),
         name_id = factor(name_id, levels = name_id)) %>%
  ggplot(aes(start, name_id, colour = party)) +
    geom_point() +
    geom_segment(aes(xend = end, yend = name_id)) +
    scale_colour_manual(values = c(Republican = 'red', Democratic = 'blue')) +
    scale_y_discrete(NULL) +
    scale_x_date(NULL, breaks = years, date_labels = "'%y") +
    theme(panel.grid.minor = element_blank())
```

## 4.
```{r}
ggplot(diamonds, aes(carat, price)) +
  geom_point(aes(colour = cut), alpha = 1/20)  +
  theme(legend.position = "bottom") +
  guides(colour = guide_legend(nrow = 1, override.aes = list(alpha = 1)))
```